---
title: "AIPW: Effects of Untrustworthy-News Exposure on 2020 Vote Outcomes"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: flatly
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = "center")
```

---

# 1. Setup

```{r packages}
#install.packages("aipw")
#install.packages("SuperLearner")
#install.packages("cobalt")
#install.packages("gridExtra")
#install.packages("kableExtra")
library(aipw)
library(SuperLearner)
library(cobalt)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(kableExtra)

set.seed(42)
```

```{r load_data}
df_raw <- read.csv("master_data_2020.csv", stringsAsFactors = FALSE)

# Drop the 162 respondents who did not complete the post-wave
# (presvote20post is NA for them — their vote status is unknown)
df <- df_raw[!is.na(df_raw$presvote20post), ]
cat("N after dropping post-wave non-respondents:", nrow(df), "\n")
```

---

# 2. Feature Engineering

Replicates the covariate set from the Python pipeline.

```{r outcomes}
# Binary outcomes from post-wave vote choice
df$voted_biden <- as.integer(trimws(df$presvote20post) == "Joe Biden")
df$voted_trump <- as.integer(trimws(df$presvote20post) == "Donald Trump")
df$turnout     <- as.integer(
  !grepl("did not vote", df$presvote20post, ignore.case = TRUE)
)
```

```{r digital_literacy}
# Digital literacy index: extract leading digit from "1 None" / "2 Little" etc.
tf_cols <- c("tf_adv", "tf_pdf", "tf_spy", "tf_wiki", "tf_cache", "tf_phishing")
extract_digit <- function(x) {
  suppressWarnings(as.numeric(sub("^(\\d+).*", "\\1", trimws(as.character(x)))))
}
tf_mat           <- sapply(df[, tf_cols], extract_digit)
df$digital_lit   <- rowMeans(tf_mat, na.rm = TRUE)
```

```{r linear_scales}
# Named-vector lookup tables for ordinal scales
ideo5_lut  <- c("Very liberal"=1, "Liberal"=2, "Moderate"=3,
                "Conservative"=4, "Very conservative"=5)
pid7_lut   <- c("Strong Democrat"=1, "Not very strong Democrat"=2,
                "Lean Democrat"=3, "Independent"=4, "Lean Republican"=5,
                "Not very strong Republican"=6, "Strong Republican"=7)
newsint_lut <- c("Hardly at all"=1, "Only now and then"=2,
                 "Some of the time"=3, "Most of the time"=4)
intuse_lut  <- c("Less often"=1, "A few times a week"=2,
                 "About once a day"=3, "Several times a day"=4)

df$ideo5_linear   <- ideo5_lut[df$ideo5]
df$pid7_linear    <- pid7_lut[df$pid7]
df$newsint_linear <- newsint_lut[df$newsint]
df$intuse_linear  <- intuse_lut[df$intuse]

# socmed_use: use regex to handle both hyphen and en-dash encodings in CSV
df$socmed_linear <- case_when(
  grepl("Less than 10",        df$socmed_use)  ~ 1L,
  grepl("10.30 min",           df$socmed_use)  ~ 2L,
  grepl("31.60 min",           df$socmed_use)  ~ 3L,
  grepl("1.2 hour",            df$socmed_use)  ~ 4L,
  grepl("2.3 hour",            df$socmed_use)  ~ 5L,
  grepl("More than 3",         df$socmed_use)  ~ 6L,
  TRUE ~ NA_integer_
)
```

```{r categorical_covariates}
# 2016 vote, condensed to four levels; Trump_2016 = baseline
df$vote16 <- case_when(
  df$presvote16post == "Hillary Clinton"                              ~ "Clinton",
  df$presvote16post == "Donald Trump"                                ~ "Trump_2016",
  is.na(df$presvote16post) |
    df$presvote16post %in% c("Did not vote", "Did not vote for President") ~ "DidNotVote",
  TRUE                                                               ~ "Other"
)

# Set reference levels to match Python baselines
df$race4  <- factor(df$race4,  levels = c("White",        "Black", "Hispanic", "Other"))
df$educ4  <- factor(df$educ4,  levels = c("College grad", "HS or less", "Some college", "Postgrad"))
df$region <- factor(df$region, levels = c("Midwest",      "Northeast", "South", "West"))
df$vote16 <- factor(df$vote16, levels = c("Trump_2016",   "Clinton", "DidNotVote", "Other"))
```

```{r complete_cases}
covariate_cols <- c(
  "age", "female", "digital_lit",
  "ideo5_linear", "pid7_linear", "socmed_linear", "newsint_linear", "intuse_linear",
  "race4", "educ4", "region", "vote16"
)

keep_cols <- c("untrustworthy_flag", "voted_biden", "voted_trump", "turnout", covariate_cols)
df_model  <- na.omit(df[, keep_cols])
cat("Analytic sample (complete cases):", nrow(df_model), "\n")

# Treatment vector and design matrix (no intercept)
A     <- df_model$untrustworthy_flag
W_mat <- model.matrix(
  ~ age + female + digital_lit +
    ideo5_linear + pid7_linear + socmed_linear + newsint_linear + intuse_linear +
    race4 + educ4 + region + vote16,
  data = df_model
)[, -1]  # drop intercept column

W_df  <- as.data.frame(W_mat)   # aipw expects a data.frame
cat("Covariates in design matrix:", ncol(W_df), "\n")
```

---

# 3. Overlap Check (Positivity Assumption)

The overlap (positivity) assumption requires P(W=1|X) ∈ (0,1) for all X in the
support. We check it by fitting a logistic regression propensity score model and
inspecting the score distributions across treatment groups.

```{r propensity_model}
ps_fit <- glm(A ~ ., data = W_df, family = binomial)
ps     <- predict(ps_fit, type = "response")

# Trim-bound diagnostics
cat("Propensity score range: [", round(min(ps),4), ",", round(max(ps),4), "]\n")
cat("Outside [0.05, 0.95]:", sum(ps < 0.05 | ps > 0.95),
    sprintf("(%.1f%%)\n", 100 * mean(ps < 0.05 | ps > 0.95)))
cat("Outside [0.10, 0.90]:", sum(ps < 0.10 | ps > 0.90),
    sprintf("(%.1f%%)\n", 100 * mean(ps < 0.10 | ps > 0.90)))
```

```{r ess}
# IPW effective sample size — collapses when extreme weights dominate
ess_t <- sum(A / ps)^2          / sum((A / ps)^2)
ess_c <- sum((1-A) / (1-ps))^2  / sum(((1-A) / (1-ps))^2)
cat(sprintf(
  "IPW ESS — Treated: %.0f/%d (%.0f%%)   Control: %.0f/%d (%.0f%%)\n",
  ess_t, sum(A),   100*ess_t/sum(A),
  ess_c, sum(1-A), 100*ess_c/sum(1-A)
))
```

```{r overlap_plots, fig.width=11, fig.height=4}
ps_df <- data.frame(
  ps    = ps,
  logit = log(ps / (1 - ps)),
  Group = factor(A, labels = c("Control (unexposed)", "Treated (exposed)"))
)

p_hist <- ggplot(ps_df, aes(x = ps, fill = Group)) +
  geom_histogram(aes(y = after_stat(density)), bins = 40,
                 alpha = 0.55, position = "identity") +
  geom_vline(xintercept = c(0.05, 0.95), linetype = "dashed") +
  scale_fill_manual(values = c("steelblue", "tomato")) +
  labs(x = "Propensity Score P(W=1|X)", y = "Density",
       title = "Propensity Score Distributions",
       subtitle = "Dashed lines = trim bounds [0.05, 0.95]",
       fill = NULL) +
  theme_bw(base_size = 12)

p_logit <- ggplot(ps_df, aes(x = logit, fill = Group)) +
  geom_histogram(aes(y = after_stat(density)), bins = 40,
                 alpha = 0.55, position = "identity") +
  scale_fill_manual(values = c("steelblue", "tomato")) +
  labs(x = "Log-Odds of Propensity Score", y = "Density",
       title = "Overlap: Log-Odds Scale",
       subtitle = "Separation here indicates covariate profiles with weak overlap",
       fill = NULL) +
  theme_bw(base_size = 12)

grid.arrange(p_hist, p_logit, ncol = 2)
```

---

# 4. Covariate Balance

Standardized mean differences (SMD) before weighting. Conventional threshold: |SMD| < 0.1.
Variables with |SMD| ≥ 0.1 flag the strongest confounders that the AIPW must adjust for.

```{r covariate_balance, fig.width=8, fig.height=7}
bal <- bal.tab(
  W_df,
  treat      = A,
  thresholds = c(m = 0.1),
  binary     = "std"
)
print(bal)

love.plot(
  bal,
  threshold   = 0.1,
  abs         = TRUE,
  colors      = c("tomato", "steelblue"),
  shapes      = c("circle", "circle filled"),
  title       = "Covariate Balance: |SMD| Before Weighting",
  sample.names = c("Unadjusted")
)
```

---

# 5. AIPW Estimation

We estimate the ATE for each outcome using:

- **Nuisance models**: logistic regression via SuperLearner (`SL.glm`)
- **Cross-fitting**: 10-fold (`k_split = 10`) to avoid in-sample overfitting bias
- **Propensity clip**: `g.bound = 0.025` → clips ê(X) to [0.025, 0.975]

```{r aipw_fit, cache=TRUE, results='hide'}
outcomes_list <- list(
  "Voted for Biden" = df_model$voted_biden,
  "Voted for Trump" = df_model$voted_trump,
  "2020 Turnout"    = df_model$turnout
)

aipw_objects <- list()

for (nm in names(outcomes_list)) {
  aipw_objects[[nm]] <- AIPW$new(
    Y              = outcomes_list[[nm]],
    A              = A,
    W              = W_df,
    Q.SL.library   = "SL.glm",
    g.SL.library   = "SL.glm",
    k_split        = 10,
    verbose        = FALSE
  )$fit()
}
```

```{r aipw_summary}
for (nm in names(aipw_objects)) {
  cat("\n===", nm, "===\n")
  aipw_objects[[nm]]$summary(g.bound = 0.025)
}
```

```{r results_table}
# Collect ATE rows into a summary table
results_df <- do.call(rbind, lapply(names(aipw_objects), function(nm) {
  obj <- aipw_objects[[nm]]
  obj$summary(g.bound = 0.025)
  res <- obj$result
  # ATE row only (third row: E[Y(1)]-E[Y(0)])
  ate_row <- res[grepl("ATE|RD|E\\[Y\\(1\\)\\]-E\\[Y\\(0\\)\\]", rownames(res),
                       ignore.case = TRUE), , drop = FALSE]
  if (nrow(ate_row) == 0) ate_row <- res[nrow(res), , drop = FALSE]
  data.frame(
    Outcome = nm,
    ATE     = round(ate_row[[1]], 4),
    SE      = round(ate_row[[2]], 4),
    CI_lo   = round(ate_row[[3]], 4),
    CI_hi   = round(ate_row[[4]], 4),
    p_value = round(ate_row[[5]], 4),
    stringsAsFactors = FALSE
  )
}))

results_df$Sig <- ifelse(results_df$p_value < 0.01, "**",
                  ifelse(results_df$p_value < 0.05, "*", ""))

kable(results_df,
      col.names = c("Outcome", "ATE", "SE", "95% CI Lower", "95% CI Upper", "p-value", ""),
      caption   = "AIPW Estimates: Effect of Untrustworthy-News Exposure on 2020 Vote  (* p<0.05, ** p<0.01)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r forest_plot, fig.width=6.5, fig.height=3.5}
ggplot(results_df, aes(x = ATE, y = Outcome, colour = ATE > 0)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lo, xmax = CI_hi), height = 0.2, linewidth = 0.9) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "black") +
  scale_colour_manual(values = c("steelblue", "tomato"), guide = "none") +
  labs(x = "Average Treatment Effect (AIPW, 95% CI)",
       y = NULL,
       title = "Effect of Untrustworthy-News Exposure on 2020 Vote Outcomes") +
  theme_bw(base_size = 12)
```

---

# 6. AIPW Diagnostics

Built-in `aipw` diagnostics: propensity score distribution and IPW weight distribution
after g.bound clipping. Extreme weights signal residual overlap problems.

```{r aipw_diagnostics, fig.width=11, fig.height=4}
for (nm in names(aipw_objects)) {
  obj <- aipw_objects[[nm]]
  obj$summary(g.bound = 0.025)
  p1 <- obj$plot.p_score()
  p2 <- obj$plot.ip_weights()
  grid.arrange(
    p1 + ggtitle(paste(nm, "— Propensity Scores")),
    p2 + ggtitle(paste(nm, "— IPW Weights")),
    ncol = 2
  )
}
```

---

# 7. Sensitivity Analysis: g.bound

We re-estimate the Voted-for-Biden ATE under tighter and looser propensity
trimming to assess sensitivity of results to the choice of clip threshold.

```{r sensitivity, cache=TRUE, results='hide'}
g_bounds <- c(0.01, 0.025, 0.05, 0.10)

biden_obj <- AIPW$new(
  Y            = df_model$voted_biden,
  A            = A,
  W            = W_df,
  Q.SL.library = "SL.glm",
  g.SL.library = "SL.glm",
  k_split      = 10,
  verbose      = FALSE
)$fit()
```

```{r sensitivity_table}
sens_rows <- lapply(g_bounds, function(gb) {
  biden_obj$summary(g.bound = gb)
  res     <- biden_obj$result
  ate_row <- res[grepl("ATE|RD|E\\[Y\\(1\\)\\]-E\\[Y\\(0\\)\\]", rownames(res),
                       ignore.case = TRUE), , drop = FALSE]
  if (nrow(ate_row) == 0) ate_row <- res[nrow(res), , drop = FALSE]
  data.frame(
    g.bound = gb,
    clip_range = sprintf("[%.3f, %.3f]", gb, 1 - gb),
    ATE    = round(ate_row[[1]], 4),
    SE     = round(ate_row[[2]], 4),
    CI_lo  = round(ate_row[[3]], 4),
    CI_hi  = round(ate_row[[4]], 4),
    p      = round(ate_row[[5]], 4)
  )
})

sens_df <- do.call(rbind, sens_rows)

kable(sens_df,
      col.names = c("g.bound", "Clip range", "ATE", "SE", "95% CI Lo", "95% CI Hi", "p"),
      caption   = "Sensitivity to propensity score clipping — Voted for Biden outcome") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

---

# Session Info

```{r session_info}
sessionInfo()
```
